Reducing iptables configuration complexity using chains

### 2014-05-04 iptables/paper.tex
add filters and target subsection placeholders
use default and custom chains

  \subsection{Chains}
    There are several predefined chains :
    \begin{itemize}
      \item INPUT
      \item OUTPUT
      \item FORWARD
      \item PREROUTING
      \item POSTROUTING
    \end{itemize}
    Defining custom chains is also possible.\\

@@

@@

\subsection{Introducing chains}
When two services (on different ports) should be available to a limited but identical list of IP addresses.
Without using chains, for every combination of port and IP a rule should be created :
\begin{verbatim}
  iptables -A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 22 -j ACCEPT
  iptables -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 22 -j ACCEPT
  iptables -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 22 -j ACCEPT

@@

When using chains, this can be much easier. Imagine, that you first check if the packet matches the destination port, and if it does, jump to a new chain, where a list of IP addresses is checked. :
\begin{verbatim}
  // create new chain admin_IP
  iptables -N admin_IP

  // add rules to chain admin_IP
  iptables -A admin_IP -s 10.100.2.3 -j ACCEPT
  iptables -A admin_IP -s 10.100.2.4 -j ACCEPT
  iptables -A admin_IP -s 10.100.2.7 -j ACCEPT
  // drop all packets that are not matched by previous rules
  iptables -A admin_IP -j DROP

>>>>

  \subsection{Default chains}
    There are several predefined chains :
    \begin{itemize}
      \item INPUT
      \item OUTPUT
      \item FORWARD
      \item PREROUTING
      \item POSTROUTING
    \end{itemize}
    Defining custom chains is also possible.\\

@@

  \subsection{Filters}
  \subsection{Targets}

@@

\subsection{Introducing custom chains}
When two services (on different ports) should be available to a limited but identical list of IP addresses.
Without using chains, for every combination of port and IP a rule should be created :
\begin{verbatim}
  iptables -A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 22 -j ACCEPT
  iptables -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 22 -j ACCEPT
  iptables -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 22 -j ACCEPT

@@

When using custom chains, this can be much easier. Imagine, that you first check if the packet matches the destination port, and if it does, jump to a new chain, where a list of IP addresses is checked. :
\begin{verbatim}
  // create new custom chain admin_IP
  iptables -N admin_IP

  // add rules to custom chain admin_IP
  iptables -A admin_IP -s 10.100.2.3 -j ACCEPT
  iptables -A admin_IP -s 10.100.2.4 -j ACCEPT
  iptables -A admin_IP -s 10.100.2.7 -j ACCEPT
  // drop all packets that are not matched by previous rules
  iptables -A admin_IP -j DROP
